  %-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Game Development} % Job title
    {\href{https://github.com/AbhiSaphire/Stay-Safe-Bot-Game}{Stay Safe Bot! Game}} % Organization
    {Personal Project} % Type
    {Mar. 2020 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The game is been developed on godot game engine with gdscript scripting language.}
        \item {Your character / player must move and avoid the enemies for as long as possible.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web-App Development} % Job title
    {\href{https://github.com/AbhiSaphire/Django-RealEstate-WebApp}{Real Estate Web-App}} % Organization
    {Web-Tech Lab Project} % Type
    {Jul. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a property trading web application using Django. This Real estate portal is basically used to deal with rich functionalities for the private sellers, buyers and real estate agents to list properties for sale or rent, search in the database.}
        \item {It includes powerful backend and security support by Django and professional looking frontend by HTML, CSS, Pillow and Bootstrap.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web-App Development} % Job title
    {\href{https://github.com/AbhiSaphire/Django-DiscussionForum}{Discussion Platform (CHARCHA)}} % Organization
    {Personal Project} % Type
    {Aug. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a discussion forum platform using Django, in which users can interact or discuss on any topic.}
        \item {Also shows real time updates with time stamps.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programming} % Job title
    {\href{https://github.com/AbhiSaphire/Web-Scrapers}{Python Web Scrapers}} % Organization
    {Personal Projects} % Type
    {Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a web crawler which lets user download or listen to songs, this web scraper crawls www.mp3download.center to search the songs.}
        \item {Developed a simple web crawler using python, which collects the products and respective links of the products from a page of amazon.in .}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Application Development} % Job title
    {\href{https://github.com/AbhiSaphire/TravelAgency}{Travel Agency Application}} % Organization
    {OOPs Lab Project} % Type
    {Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a travel agency software in C++, which has 2 modules Admin and End-user. Having functionalities of choosing holiday packages, destinations and then paying for trip.}
        \item {Project mainly focuses on Object Oriented Programming.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Application Development} % Job title
    {\href{https://github.com/AbhiSaphire/FeedbackManagement}{Feedback Management System}} % Organization
    {DS and Algo Lab Project} % Location
    {Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a feedback management software using C, which have basic features of giving feedbacks for employers.}
        \item {Project mainly focuses on Data Structures and Algorithms.}
        \github{AbhiSaphire/FeedbackManagement}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {}

%----------------------------------------------------------
\end{cventries}
